Poincar\'e--Friedrichs constants over domains with shellable triangulations

### 2024-06-28 draft.tex
Update on Overleaf.

@@

\begin{align*}
    G_\ell(x,y) 
    &\leq 
    \int_{0}^{\frac{D}{|x-y|}} \tau^{n-\ell} (\tau+1)^{\ell-1} \,d\tau
    \\
    &\leq 
    \frac{|x-y|}{D}
    \int_{0}^{\frac{D}{|x-y|}} \frac{D}{|x-y|} \tau^{n-\ell} (\tau+1)^{\ell-1} \,d\tau
    .
\end{align*}
\begin{align*}
    G_\ell(x,y)^{p} 
    &\leq 
    \frac{|x-y|}{D}
    \int_{0}^{\frac{D}{|x-y|}} \frac{D^{p}}{|x-y|^{p}} \tau^{pn-p\ell} (\tau+1)^{p\ell-p} \,d\tau
    \\&\leq 
    \frac{|x-y|}{D}
    \frac{D^{p}}{|x-y|^{p}} \int_{0}^{\frac{D}{|x-y|}} (\tau+1)^{pn-p} \,d\tau
    \\&\leq 
    \frac{D^{p-1}}{|x-y|^{p-1}} \left( \left( \frac{D}{|x-y|} + 1 \right)^{pn-p+1} - 1 \right)
    \\&\leq 
    \frac{D^{p-1}}{|x-y|^{p-1}} \left( 2^{pn-p+1} \left( \frac{D}{|x-y|} \right)^{pn-p+1} - 1 \right)
    \\&\leq 
    2^{pn-p+1} \frac{D^{pn}}{|x-y|^{pn}} - \frac{D^{p-1}}{|x-y|^{p-1}}
    .
\end{align}

@@

In order to see other properties of the operators, we apply a different change of variables. 
Let us write this in detail for the operator $R_{\ell}$. 
We substitute $y$ by the new variable $a=y+t(x-y)$.
Whence $da = (1-t)^n dy$ and $t(x-y) = a-y$ and $x-y = (a-y)/t$ and $x - (a-x)/t = y$
\begin{align*}
    \Bogov_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\&= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+(x-y)-(x-y)+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\&= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(x+(t+1)(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} (t+1)^{n}
    \chi_{\Omega}\left(a\right) 
    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
\end{align*}
Then we substitute $1-s = 1/(t+1)$, that is, $s = t/(t+1)$:
Whence $t = \left( 1/s-1 \right)^{-1}$.
\begin{align*}
    \Bogov_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell} \left( 1/s-1 \right)^{\ell-1} (t+1)^{n}
    \chi_{\Omega}\left(a\right) 
    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
    \\
    &= 
    .
\end{align*}

Then we substitute $s = (t-1)/t$:
\begin{align*}
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{-n+\ell-1} 
    \chi_{\Omega}\left(a\right)
    \frac{(a-y)}{t} \lrcorner u(x+(a-x)/t) \,dt\,da 
    \\
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
    .
\end{align*}
Then we substitute $s = (t-1)/t$:
\begin{align*}
    \Bogov_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
    \\
    &= 
    - \int \int_{1}^\infty s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
    \\
    &=
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
We copy a statement by McIntosh and Costabel:
\begin{align*}
    \Bogov_{\ell} u(x) 
    = 
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
$a = y + t(x-y)$
$s = \frac{t}{t-1}$
From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $\Bogov_{\ell} u(x)$ is smooth with support contained in $\overline\Omega$ as well.

From this form of $\Bogov_{\ell}$, because of the unbounded interval of integration in $t$, one cannot immediately conclude that $\Bogov_{\ell}$ maps ${C^\infty}$ functions to ${C^\infty}$ functions.
But if $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$, one sees that $\Bogov_{\ell} u$ is ${C^\infty}$ on 
$\bbR^n\setminus\supp\chi_{\Omega}$, and that 
$\Bogov_{\ell} u(x)=0$ unless $x$ lies in the starlike hull of $\supp u$ with respect to $B$. 
Thus if $\Omega$ is open and starlike with respect to $B$, then   
$u\in{C^\infty_c}(\Omega,\Alt^\ell)$ implies $\supp \Bogov_{\ell} u \subset\Omega$, and, if $\Omega$ is bounded, then
$u\in{C^\infty}_{\overline\Omega}(\bbR^n,\Alt^\ell)$ implies $\supp \Bogov_{\ell} u \subset\overline\Omega$. 
The fact that $\Bogov_{\ell}$ indeed maps 
${C^\infty_c}(\bbR^n,\Alt^\ell)$ to ${C^\infty_c}(\bbR^n,\Alt^{\ell-1})$ will be a consequence of Theorem~\ref{T:pseudo} below.

@@

Integrating \eqref{eq:Cartan} from $0$ to $1$ and comparing with \eqref{eq:regPoincare}, 
we find the homotopy relations, valid for all $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$ 
\begin{equation}
\begin{aligned}
\label{eq:dR+Rd=1}
 dR_{\ell} u + R_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
 R_1 du &= u - \left(\chi_{\Omega},u\right)\; &&(\ell=0)\;;\\
 dR_nu &=u &&(\ell=n)\;.
\end{aligned}
\end{equation}
One could be tempted to integrate Cartan's formula from $1$ to $\infty$ and compare with \eqref{eq:Bogo}, thus formally obtaining a similar homotopy relation for $\Bogov_{\ell}$ directly. The result is indeed true except for $\ell=n$, but for a rigorous proof we prefer to use the duality relation \eqref{eq:dualRT} to deduce corresponding anticommutativity relations for $\Bogov_{\ell}$ from the relations \eqref{eq:dR+Rd=1} which are already proved. Here is what one obtains for $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$:
\begin{equation}
\begin{aligned}
\label{eq:dT+Td=1}
  d\Bogov_{\ell} u + T_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
  T_1 du &= u \; &&(\ell=0)\;;\\
 dT_n u &=u - (\int\! u)\star\chi_{\Omega}&&(\ell=n)\;.
\end{aligned}
\end{equation}
Here we consider $\chi_{\Omega}$ as an element of ${C^\infty_c}(\bbR^n,\Alt^0)$, so that for another $0$-form $u$ we have the $L^2$ scalar product $\left(\chi_{\Omega},u\right)=\int\chi_{\Omega}(a)u(a)da$, and $\star\chi_{\Omega}$ is the $n$-form $\chi_{\Omega}(x)dx_1\wedge\dots\wedge dx_n$.

@@

If we correspondingly extend the definitions of $R_{\ell}$ and $\Bogov_{\ell}$ by
$$
\begin{aligned}
  R_0u &:=\left(\chi_{\Omega},u\right)\,\text{ for $0$-forms }u\,, &
  R_{n+1} &:=0\,,\\
  T_{n+1}u &:= \star(u\chi_{\Omega}) \,\text{ for }u\in\bbR\,,  &
  T_0 &:= 0\,,
\end{aligned}
$$
then we can write the relations \eqref{eq:dR+Rd=1} and \eqref{eq:dT+Td=1} simply as
\begin{equation}\label{eq:R&T&d}
 \overline d\,R_{\ell} u + R_{\ell+1} \,\overline d u  = u
 \quad \text{ and }\quad
 \underline d\,\Bogov_{\ell} u + T_{\ell+1} \,\underline du = u\quad \text{ for all }\;
  0\le\ell\le n.
\end{equation}

@@

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{hyperref}         % For hypertext links

\input{header}

\begin{document}

Given $a \in \Omega$, we introduce the potential operator 
    \Poinc_{\ell,a} u(x) 
    &:= 
    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
By definition,
    \Poinc_{\ell} u(x) 
    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da\;
We study the interaction of the potential operator with the exterior derivative in more detail.
Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$ with $\supp u \subseteq \overline\Omega$.
We rewrite the potential,
    \Poinc_{\ell,a} u(x) 
    &= 
    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    (x-a)\lrcorner 
    \sum_{\sigma \in \Sigma(k,n)}
    \int_{0}^{1} 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
    \int_{0}^{1} 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
and compute its exterior derivative:
    \cartan \Poinc_{\ell,a} u(x) 
    &= 
    \ell
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
    \int_{0}^{1} 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
    \int_{0}^{1} 
    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
We write the exterior derivative of $u$ as 
    \cartan u(x)
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \frac{ \partial u }{\partial x_{j}}(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
and apply the potential operator to this result, which gives 
    \Poinc_{\ell+1,a} \cartan u(x)
    &=
    (x-a)\lrcorner 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
    \;\cartanx^{j} \wedge \cartanx^{\sigma}
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
    \;\cartanx^{\sigma}
    - 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
    (-1)^{i-1}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
We add the exterior derivative of the potential and the potential of the exterior derivative.
Taking into account cancellations, this gives the identity 
    \cartan \Poinc_{\ell,a} u(x)
    \Poinc_{\ell+1,a} \cartan u(x)
    \ell
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
    \int_{0}^{1} 
    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
    \int_{0}^{1} 
    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
    \cartanx^{\sigma}
    - 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
    (-1)^{i-1}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
    \int_{0}^{1} 
    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
    \cartanx^{\sigma}
    \sum_{\sigma \in \Sigma(k,n)} 
    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
    \sum_{\sigma \in \Sigma(k,n)} 
    u_{\sigma}(x) \cartanx^{\sigma}
    u(x)
In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell,a} u = u$.

@@

\begin{align*}
    G_\ell(x,y) 
    &\leq 
    \int_{0}^{\frac{D}{|x-y|}} \tau^{n-\ell} (\tau+1)^{\ell-1} \,d\tau
    \\
    &\leq 
    \frac{|x-y|}{D}
    \int_{0}^{\frac{D}{|x-y|}} \frac{D}{|x-y|} \tau^{n-\ell} (\tau+1)^{\ell-1} \,d\tau
    .
\end{align*}
\begin{align*}
    G_\ell(x,y)^{p} 
    &\leq 
    \frac{|x-y|}{D}
    \int_{0}^{\frac{D}{|x-y|}} \frac{D^{p}}{|x-y|^{p}} \tau^{pn-p\ell} (\tau+1)^{p\ell-p} \,d\tau
    \\&\leq 
    \frac{|x-y|}{D}
    \frac{D^{p}}{|x-y|^{p}} \int_{0}^{\frac{D}{|x-y|}} (\tau+1)^{pn-p} \,d\tau
    \\&\leq 
    \frac{D^{p-1}}{|x-y|^{p-1}} \left( \left( \frac{D}{|x-y|} + 1 \right)^{pn-p+1} - 1 \right)
    \\&\leq 
    \frac{D^{p-1}}{|x-y|^{p-1}} \left( 2^{pn-p+1} \left( \frac{D}{|x-y|} \right)^{pn-p+1} - 1 \right)
    \\&\leq 
    2^{pn-p+1} \frac{D^{pn}}{|x-y|^{pn}} - \frac{D^{p-1}}{|x-y|^{p-1}}
    .
\end{align*}

@@

In order to see other properties of the operators, we apply a different change of variables. 
Let us write this in detail for the operator $R_{\ell}$. 
We substitute $y$ by the new variable $a=y+t(x-y)$.
Whence $da = (1-t)^n dy$ and $t(x-y) = a-y$ and $x-y = (a-y)/t$ and $x - (a-x)/t = y$
\begin{align*}
    \Poinc_{\ell} u(x) 
    &= 
    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\&= 
    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+(x-y)-(x-y)+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\&= 
    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(x+(t+1)(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &= 
    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1} (t+1)^{n}
    \chi_{\Omega}\left(a\right) 
    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
\end{align*}
Then we substitute $1-s = 1/(t+1)$, that is, $s = t/(t+1)$:
Whence $t = \left( 1/s-1 \right)^{-1}$.
\begin{align*}
    \Poinc_{\ell} u(x) 
    &= 
    \int \int_{0}^{1} (t-1)^{n-\ell} \left( 1/s-1 \right)^{\ell-1} (t+1)^{n}
    \chi_{\Omega}\left(a\right) 
    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
    \\
    &= 
    .
\end{align*}

Then we substitute $s = (t-1)/t$:
\begin{align*}
    &= 
    \int \int_{0}^{1} (t-1)^{n-\ell}t^{-n+\ell-1} 
    \chi_{\Omega}\left(a\right)
    \frac{(a-y)}{t} \lrcorner u(x+(a-x)/t) \,dt\,da 
    \\
    &= 
    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
    .
\end{align*}
Then we substitute $s = (t-1)/t$:
\begin{align*}
    \Poinc_{\ell} u(x) 
    &= 
    \int \int_{0}^{1} s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
    \\
    &= 
    - \int \int_{0}^{1} s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
    \\
    &=
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
We copy a statement by McIntosh and Costabel:
\begin{align*}
    \Poinc_{\ell} u(x) 
    = 
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
$a = y + t(x-y)$
$s = \frac{t}{t-1}$
From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $\Poinc_{\ell} u(x)$ is smooth with support contained in $\overline\Omega$ as well.

From this form of $\Poinc_{\ell}$, because of the unbounded interval of integration in $t$, one cannot immediately conclude that $\Poinc_{\ell}$ maps ${C^\infty}$ functions to ${C^\infty}$ functions.
But if $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$, one sees that $\Poinc_{\ell} u$ is ${C^\infty}$ on 
$\bbR^n\setminus\supp\chi_{\Omega}$, and that 
$\Poinc_{\ell} u(x)=0$ unless $x$ lies in the starlike hull of $\supp u$ with respect to $B$. 
Thus if $\Omega$ is open and starlike with respect to $B$, then   
$u\in{C^\infty_c}(\Omega,\Alt^\ell)$ implies $\supp \Poinc_{\ell} u \subset\Omega$, and, if $\Omega$ is bounded, then
$u\in{C^\infty}_{\overline\Omega}(\bbR^n,\Alt^\ell)$ implies $\supp \Poinc_{\ell} u \subset\overline\Omega$. 
The fact that $\Poinc_{\ell}$ indeed maps 
${C^\infty_c}(\bbR^n,\Alt^\ell)$ to ${C^\infty_c}(\bbR^n,\Alt^{\ell-1})$ will be a consequence of Theorem~\ref{T:pseudo} below.

@@

Integrating \eqref{eq:Cartan} from $0$ to $1$ and comparing with \eqref{eq:regPoincare}, 
we find the homotopy relations, valid for all $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$ 
\begin{equation}
\begin{aligned}
\label{eq:dR+Rd=1}
 dR_{\ell} u + R_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
 R_1 du &= u - \left(\chi_{\Omega},u\right)\; &&(\ell=0)\;;\\
 dR_nu &=u &&(\ell=n)\;.
\end{aligned}
\end{equation}
One could be tempted to integrate Cartan's formula from $1$ to $\infty$ and compare with \eqref{eq:Bogo}, thus formally obtaining a similar homotopy relation for $\Poinc_{\ell}$ directly. The result is indeed true except for $\ell=n$, but for a rigorous proof we prefer to use the duality relation \eqref{eq:dualRT} to deduce corresponding anticommutativity relations for $\Poinc_{\ell}$ from the relations \eqref{eq:dR+Rd=1} which are already proved. Here is what one obtains for $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$:
\begin{equation}
\begin{aligned}
\label{eq:dT+Td=1}
  d\Poinc_{\ell} u + \Poinc_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
  T_1 du &= u \; &&(\ell=0)\;;\\
 dT_n u &=u - (\int\! u)\star\chi_{\Omega}&&(\ell=n)\;.
\end{aligned}
\end{equation}
Here we consider $\chi_{\Omega}$ as an element of ${C^\infty_c}(\bbR^n,\Alt^0)$, so that for another $0$-form $u$ we have the $L^2$ scalar product $\left(\chi_{\Omega},u\right)=\int\chi_{\Omega}(a)u(a)da$, and $\star\chi_{\Omega}$ is the $n$-form $\chi_{\Omega}(x)dx_1\wedge\dots\wedge dx_n$.

@@

If we correspondingly extend the definitions of $R_{\ell}$ and $\Poinc_{\ell}$ by
$$
\begin{aligned}
  R_0u &:=\left(\chi_{\Omega},u\right)\,\text{ for $0$-forms }u\,, &
  R_{n+1} &:=0\,,\\
  T_{n+1}u &:= \star(u\chi_{\Omega}) \,\text{ for }u\in\bbR\,,  &
  T_0 &:= 0\,,
\end{aligned}
$$
then we can write the relations \eqref{eq:dR+Rd=1} and \eqref{eq:dT+Td=1} simply as
\begin{equation}\label{eq:R&T&d}
 \overline d\,R_{\ell} u + R_{\ell+1} \,\overline d u  = u
 \quad \text{ and }\quad
 \underline d\,\Poinc_{\ell} u + \Poinc_{\ell+1} \,\underline du = u\quad \text{ for all }\;
  0\le\ell\le n.
\end{equation}

@@

\begin{align}
        v_0 + \langle v_k - v_0, v_{k-1} - v_0, \dots, v_1 - v_0 \rangle,
        \\
        \langle v_n - v_{k+1}, \dots, v_n - v_{n-1} \rangle + v_{0},
        \\
        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ),
        \\
        v_0 + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
        \\
        x = v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
    \end{align}
    \begin{align}
        v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
        +
        \sum_{i=1}^{k} \lambda_{i} v_i 
        +
        \sum_{i=k+1}^{n-1} \lambda_{i} v_n
        -
        \sum_{i=k+1}^{n-1} \lambda_{i} v_i
    \end{align}
    \begin{align}
        v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
        +
        \sum_{i=1}^{k} \lambda_{i} v_i 
        +
        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i
        +
        \sum_{i=k+1}^{n-1} \lambda_{i} v_n
    \end{align}

\end{document}
